%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------
\cvsection{Research \& Working Experience}
%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------
\begin{cventries}
\cventry
{Prof. Chin-Hui Yu's Lab, Department of Chemistry, National Tsing Hua University} % Institution
{Undergraduate Research \& Research Assistant}
{Hsinchu, Taiwan} % Location
{Jan. 2017 -- Mar. 2019}
{
\begin{minipage}{\textwidth}
\textbf{Research Project Topic:}\\
\textit{"Using Constrained Multi-Coordinate Driven Method to Study the Regioselectivity in Hydroxybenzyl Alcohol Formation Under Alkaline Aqueous Environments"}
\begin{itemize}
    \item Using the constrained reduced dimensionality (CRD) algorithm, incoporate with Gaussian 09, to study how phenol and formaldehyde forms Hydroxybenzyl Alcohol in Alkaline Aqueous Environment. 
\end{itemize}
\textbf{Computational Cluster \& Network Management:}
\begin{itemize}
    \item Managed and maintained the Linux-based computer cluster(30+ PCs) in our lab.
    \item Successfully compiled and deployed Gaussian 16 in our computational cluster.
\end{itemize}
\end{minipage}
}

%------------------------------------------------

\cventry
{Prof. Li-Kang Chu's Lab, Department of Chemistry, National Tsing Hua University}
{Master Degree Research}
{Hsinchu, Taiwan}
{Sep. 2019 -- Aug. 2021}
{
\begin{minipage}{\textwidth}
\textbf{Thesis Topic:}\\
\textit{"Investigating the Protein Dynamics of Human Serum Albumin in Hypothermic and Normalthermic Conditions with Temperature Jump"}
\begin{itemize}
    \item Developed a tryptophan-based fluorescence temperature jump system to study the thermally-induced dynamic process of human serum albumin.
\end{itemize}
\textbf{Side Project 1: Nanosecond Transient Absorption Spectrometer}
\begin{itemize}
    \item Constructed a nanosecond transient absorption spectroscopy system which uses ICCD as detector.
    \item Programmed an automation acquisition script in PI's WinSpec to automatically acquire the spectrum.
\end{itemize}
\textbf{Side Project 2: Upgrade the Data Acquisition Part of a Stopped-flow Apparatus}
\begin{itemize}
    \item Replace the ADC card on an old stopped-flow apparatus, and redo the data acquisition components.
    \item Developed a new software in Java, including the data collection and the user intrface.
\end{itemize}
\end{minipage}
}

%------------------------------------------------
\cventry
{Dr. Kuo-Hua Huang's Lab, Institute of Molecular Biology, Academia Sinica}
{Research Assistant}
{Taipei, Taiwan}
{Sep. 2021 -- Aug. 2022}
{
\begin{minipage}{\textwidth}
\textbf{Research Project Topic:}\\
\textit{"Constructing Virtual Animal Models and Virtual Reality Environment to Allow Future Study on the Roles of Reciprocal Interaction in Zebrafish Social Behavior"}
\begin{itemize}
    \item Constructed a virtual zebrafish models in Blender, and a virtual reality(VR) environment in Unity.
    \item Developed a close-loop VR system, including images acquisition, real-time image processing, and VR updating.
    \item Utilized Python to analyze the behavior motif of freely-swimming zebrafish to make the animation more realistic.
\end{itemize}
\end{minipage}
}

\end{cventries}

%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------
\cvsection{Teaching Experience}
%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------
\begin{cventries}
%------------------------------------------------
\cventry
{Center for General Education, National Tsing Hua University}
{Volunteer Teaching Assistant of Undergraduate Courses}
{Hsinchu, Taiwan}
{2014 Fall -- 2016 Spring}
{Forensic Science and Crime Prevention(\textit{2014 Fall}, \textit{2015 Fall}) \& Crime Investigation Technology (\textit{2015 Spring}, \textit{2016 Spring})}

\cventry
{Department of Chemistry, National Tsing Hua University}
{Teaching Assistant of Undergraduate Courses}
{Hsinchu, Taiwan}
{2019 Fall -- 2020 Spring}
{Physical Chemistry Laboratory \Romannum{1} (\textit{2019 Fall}) \& Physical Chemistry \Romannum{2} (\textit{2020 Spring})}
\end{cventries}